Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games

### 2024-02-18 Paper/paper.tex
improved section "The Problem"

	\section{The Problem} \label{sec:theProblem}
	Blind players encounter many different barriers when playing visual-centric digital games which often rely mainly on graphical interfaces and visual cues. 
	Additionally, games have different perspectives such as top-down, first-person, and third-person views, where all three views give the player unique challenges in navigating within game environments, understanding game objectives and interacting with in-game elements like players or objects.
	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) which still represent a great challenge for both players and developers.
	%TODO rewrite

@@

	\autoref{fig:seven-themes} gives a great overview what accessibility features and assistant tools are still missing and in which direction the gaming industry should focus.

>>>>

	\section{The Problem} \label{sec:theProblem}
	Blind players encounter many different barriers when playing visual-centric digital games which often rely mainly on graphical interfaces and visual cues. 
	Additionally, games have different perspectives such as top-down, first-person, and third-person views, where all three views give the player unique challenges in navigating within game environments, understanding game objectives and interacting with in-game elements like players or objects.

	Popular games, such as \emph{The Legend of Zelda} rely mainly on visuals.
	For blind players, this is obviously a big problem because they miss a lot of important information on how to complete tasks or what is happening around them.

	As \textcite{goncalves_my_2023} states, players express feelings of frustration, telling their viewers the need for more and better accessibility features, so that everyone including blind players can have a great game experience.

	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) which still represent a great challenge for both players and developers.

@@

	\autoref{fig:seven-themes} gives a great overview what accessibility features are still missing and in which direction the gaming industry should focus.
